03-study area

### 2018-08-07 02_scripts/08_prediction.Rmd
update scripts

@@

maps = imap(raster_list_wgs84[c(15, 16, 18, 19)], ~ levelplot( 
  .x[["defoliation"]], 
  main = glue::glue("{tools::toTitleCase(.y)}: Predicted defoliation of trees (in %)"), 
  margin = FALSE,                             
  between = list(x = 0.0, y = 0.0), 
  at = seq(30, 80, length.out = 100),
  colorkey = list(
    width = 0.75,                       
    space = 'right',  
    labels = list(#at = c(0, 25, 50, 75, 100),
                font = 4),      
    axis.line = list(col = 'black')
  ),
  par.strip.text = list(col = "white", cex = 1.2),    
  col.regions = viridis)    
)
```

@@

@@

patchwork::wrap_plots(hists_all)
```

>>>>

Plot title only

@@

maps = imap(raster_list_wgs84[c(15, 16, 18, 19)], ~ levelplot( 
  .x[["defoliation"]], 
  #main = glue::glue("{tools::toTitleCase(.y)}: Predicted defoliation of trees (in %)"), 
  main = glue::glue("{tools::toTitleCase(.y)}"), 
  margin = FALSE,                             
  between = list(x = 0.0, y = 0.0), 
  at = seq(30, 80, length.out = 100),
  colorkey = list(
    width = 0.75,                       
    space = 'right',  
    labels = list(#at = c(0, 25, 50, 75, 100),
                font = 4),      
    axis.line = list(col = 'black')
  ),
  par.strip.text = list(col = "white", cex = 1.2),    
  col.regions = viridis)    
)
```

@@

Descriptive title

maps = imap(raster_list_wgs84[c(15, 16, 18, 19)], ~ levelplot( 
  .x[["defoliation"]], 
  main = glue::glue("{tools::toTitleCase(.y)}: Predicted defoliation of trees (in %)"), 
  #main = glue::glue("{tools::toTitleCase(.y)}"), 
  margin = FALSE,                             
  between = list(x = 0.0, y = 0.0), 
  at = seq(30, 80, length.out = 100),
  colorkey = list(
    width = 0.75,                       
    space = 'right',  
    labels = list(#at = c(0, 25, 50, 75, 100),
                font = 4),      
    axis.line = list(col = 'black')
  ),
  par.strip.text = list(col = "white", cex = 1.2),    
  col.regions = viridis)    
)
```

```{r}
png("../03_figures/results/predictions_demon_plots_descriptive_title.png", units = "in", width = 13, height = 9.21, res = 300)
gridExtra::grid.arrange(grobs = maps, nrow = 2, ncol = 2)
dev.off()

@@

hists_grid = patchwork::wrap_plots(hists_all)

cowplot::save_plot(hists_grid, filename = 
                   "../03_figures/results/predictions_demon_plots_hists.png", 
                   ncol = 2, nrow = 2,
                   )
```

# PNG to PDF conversion

Converts all pngs in the specified folder to pdfs. 
`&&` makes the "convert" call conditional on `cd`.
`exec` reduces memory waste of shell.
Uses "GNU parallel" library for parallel jobs and the `convert` function from the `ImageMagick` library.

```{r png to pdf, echo = FALSE, eval = FALSE}
# system("cd /home/patrick/PhD/papers/03_hyperspectral/03_figures/data && exec ls -1 *.png |
#        parallel convert '{}' '{.}.pdf'")

system("cd /home/patrick/PhD/papers/03_hyperspectral/03_figures/results/ && exec ls -1 *.png | 
       parallel convert '{}' '{.}.pdf'")

# copy to presentation folder
# file_copy("/home/patrick/PhD/papers/01_model_comparison/04_figures/02_results/cv_boxplots_final.png",
#           "/home/patrick/PhD/presentations/paper1/figs/cv_boxplots_final.png",
#           overwrite = TRUE)
```

# Session Info

```{r}
sessionInfo()
```

### 2018-08-07 02_scripts/09_vis_sp_partitions.Rmd
update scripts

```{r}
devtools::install_github("mlr-org/mlr@fix-create-resamp-plots")
library(mlr)
library(tibble)
library(data.table)
library(cowplot)
library(ggrepel)
library(magrittr)
```

@@

# We need to subset the data with geom_label_repel to only plot 4 repels
# We need to make sure to select one instance of every plot
plist[["Plots"]] = purrr::map(plist[["Plots"]], ~ .x + 
                         geom_label_repel(aes(x = X, y = Y, label = plot), 
                                          min.segment.length = unit(1, "lines"),
                                          data = subset(.x$data, rownames(.x$data) %in% 
                                                          c(200, 700, 1100, 1400))) +
                           labs(y = "", x = "") +
                           #theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) +
                           #hrbrthemes::theme_ipsum_rc(plot_margin = margin(0, 0, 0, 0))
                       )

@@

```{r}
data = readRDS("/data/patrick/mod/hyperspectral/data_clean_with_indices/data_clean_standardized_bf2.rda")
coords = readRDS("/data/patrick/mod/hyperspectral/data_clean_with_indices/data_clean_standardized_bf2-coords.rda")

data = data[[4]]
coords = coords[[4]]

@@

task = makeRegrTask(id = "oiartzun", data = data, 
                    target = "defoliation", coordinates = coords)

resamp_sp <- readRDS("/data/patrick/mod/hyperspectral/spcv/luiando_xgboost.rda")

plist <- createSpatialResamplingPlots(task, list("SpCV" = resamp_sp),
                                      crs = 32630, repetitions = 1, point.size = 1.5,
                                      #y.axis.breaks = c(42.8, 43.2), 
                                      #x.axis.breaks = c(-2, -3),
                                      axis.text.size = 18)

plot_grid(plot)
```

@@

```{r png to pdf, echo = FALSE, eval = FALSE}
library(furrr)
library(magick)
imgs = list.files("/home/patrick/PhD/papers/01_model_comparison/04_figures/01_data", 
                  pattern = ".png", full.names = TRUE)

>>>>

```{r}
devtools::install_github("mlr-org/mlr@fix-create-resamp-plots")
library(mlr)
library(tibble)
library(data.table)
library(cowplot)
library(ggrepel)
library(magrittr)
library(purrr)
```

@@

# We need to subset the data with geom_label_repel to only plot 4 repels
# We need to make sure to select one instance of every plot
plist[["Plots"]] = purrr::map(plist[["Plots"]], ~ .x + 
                         geom_label_repel(aes(x = X, y = Y, label = plot), 
                                          min.segment.length = unit(1, "lines"),
                                          data = subset(.x$data, rownames(.x$data) %in% 
                                                          c(200, 700, 1100, 1400))) +
                           labs(y = "", x = "") 
                           #theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) +
                           #hrbrthemes::theme_ipsum_rc(plot_margin = margin(0, 0, 0, 0))
                       )

@@

Visualize partitions for all four plots and then take only fold 1 of each.

```{r}

all = imap(c("laukiz1", "laukiz2", "luiando", "oiartzun"), ~ {
  data = readRDS("/data/patrick/mod/hyperspectral/data_clean_with_indices/data_clean_standardized_bf2.rda")
  coords = readRDS("/data/patrick/mod/hyperspectral/data_clean_with_indices/data_clean_standardized_bf2-coords.rda")

  data = data[[.y]]
  coords = coords[[.y]]

@@

  task = makeRegrTask(id = "data", data = data, 
                      target = "defoliation", coordinates = coords)

  resamp_sp <- readRDS(glue::glue("/data/patrick/mod/hyperspectral/spcv/{.x}_xgboost.rda"))

  plist <- createSpatialResamplingPlots(task, list("SpCV" = resamp_sp),
                                        crs = 32630, repetitions = 1, point.size = 1.5,
                                        y.axis.breaks = c(43.3541, 43.353, 43.2648, 43.0955), 
                                        x.axis.breaks = c(-2.93, -2.9293, -2.99577,
                                                          -1.845),
                                        axis.text.size = 18)
})

plots = plot_grid(all[[1]][["Plots"]][[1]],
                  all[[2]][["Plots"]][[1]],
                  all[[3]][["Plots"]][[1]],
                  all[[4]][["Plots"]][[1]],
                  labels = c("Fold 1 (Laukiz 1)", "Fold 1 (Laukiz 2)",
                             "Fold 3 (Luiando)", "Fold 4 (Oiartzun)"),
                  nrow = 1, ncol = 4)

save_plot(plots, filename = "../03_figures/data/spcv_folds_demon_plots.png",
          ncol = 4, nrow = 1)
```

@@

```{r png to pdf, echo = FALSE, eval = FALSE}
library(furrr)
library(magick)
imgs = list.files("/home/patrick/PhD/papers/03_hyperspectral/03_figures/data", 
                  pattern = ".png", full.names = TRUE)
